Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-13 sas2015/content/background.tex
fixes to previous fixes

\subsection{IFDS}\label{sec:bgifds}
The IFDS framework~\cite{reps1995precise} is a precise and efficient algorithm for data-flow analysis
%. IFDS was developed in 1995 by T.\,Reps, S.\,Horwitz, and M.\,Sagiv at the University of Wisconsin and
that has been used to solve a variety of data-flow analysis problems~\cite{bodden2013spl,naeem2008typestate,DBLP:conf/birthday/KreikerRRSWY13,tripp2009taj}.
The IFDS framework is an instance of the \textit{functional approach} to data-flow analysis~\cite{pnueli1981two}
because it constructs summaries of the effects of called procedures.
The IFDS framework is applicable to \textit{interprocedural} data-flow problems whose domain is a \textit{subset} of a \textit{finite} set $D$,
and whose data-flow functions are \textit{distributive}.
A function $f$ is distributive if 
$f(x_1\sqcap x_2)=f(x_1)\sqcap f(x_2)$.

>>>>

\subsection{IFDS}\label{sec:bgifds}
The IFDS framework~\cite{reps1995precise} is a precise and efficient algorithm for data-flow analysis
%. IFDS was developed in 1995 by T.\,Reps, S.\,Horwitz, and M.\,Sagiv at the University of Wisconsin and
that has been used to solve a variety of data-flow analysis problems~\cite{bodden2013spl,naeem2008typestate,DBLP:conf/birthday/KreikerRRSWY13,tripp2009taj}.
The IFDS framework is an instance of the \textit{functional approach} to data-flow analysis~\cite{pnueli1981two}
because it constructs summaries of the effects of called procedures.
The IFDS framework is applicable to \textit{interprocedural} data-flow problems whose domain is \textit{subsets} of a \textit{finite} set $D$,
and whose data-flow functions are \textit{distributive}.
A function $f$ is distributive if 
$f(x_1\sqcap x_2)=f(x_1)\sqcap f(x_2)$.

### 2015-03-13 sas2015/content/impl.tex
fixes to previous fixes

%\otodo{Give the list of criteria explicitly in the proof in the appendix.}
%\begin{enumerate}
	%\item There is a representation for the identity and top functions.
  %\item The representation is closed under the meet and composition operations.
  %\item The micro functions form a finite-height lattice.
  %\item The apply, meet, composition, and equality-check operations can be computed in constant time (independent of $E$ and $D$).
  %\item There is a constant bound on the storage space for a micro function representation.
%\end{enumerate}
%We prove these conditions with the following lemma:
\begin{restatable}{lemma}{efficient}\label{lem:efficient}
  The correlated-call representation of a micro function is efficient according to the IDE criteria and the required operations
  on micro-functions can be computed in time $O(\rcc T)$.
\end{restatable}

>>>>

%\otodo{Give the list of criteria explicitly in the proof in the appendix.}
%\begin{enumerate}
	%\item There is a representation for the identity and top functions.
  %\item The representation is closed under the meet and composition operations.
  %\item The micro functions form a finite-height lattice.
  %\item The apply, meet, composition, and equality-check operations can be computed in constant time (independent of $E$ and $D$).
  %\item There is a constant bound on the storage space for a micro function representation.
%\end{enumerate}
%We prove these conditions with the following lemma:
\begin{restatable}{lemma}{efficient}\label{lem:efficient}
  The correlated-call representation of a micro function is efficient according to the IDE criteria~\cite{sagiv1996precise} and the required operations
  on micro-functions can be computed in time $O(\rcc T)$.
\end{restatable}
